Automatically generated NE tagged corpora for English and Hungarian

### 2012-03-25 paper/engNERwiki.tex
E.

% Eszter: ehhez a felső listához hivatkozzam Nothmant? A fele tőle jön, viszont mi máshogy csináltuk kicsit.
Our solution is similar to Nothman's \shortcite{Nothman:08}. Instead of a trie, however, we use a set, albeit with more alias types. We expect more precise tagging from our slightly more rigorous solution.

@@

\begin{description}
\item[Derived words] According to the CoNLL guidelines, word derived from NEs are tagged as \texttt{MISC}. We complied with this rule by tagging each entity whose head is not a noun, as well as when the link's anchor text is not contained in the entity's name, as \texttt{MISC}. The most prominent example for such entities are nationalities, which can be linked to their home country, a \texttt{LOC}; e.g.~\textit{Turkish} to \textit{Turkey}. Our solution assigns the correct tag to these entities.
\item[First word in a sentence] As first words are always capitalized, labeling them is difficult if they are unlinked and not contained in the entity alias set. We base the decision on the POS tag of the first word: if it is NNP, we tag it as UNK; otherwise, O.
\item[Reference cleansing] Page titles and anchor texts may contain more than just the entity name. Personal titles are part of the entity name in Wikipedia, but not in CoNLL, and punctuation marks around the entity may become part of the link by mistake. We tag all punctuation marks after the entity name as \texttt{O}.

>>>>

Our solution is similar to Nothman's \shortcite{Nothman:08}. Instead of a trie, however, we use a set, albeit with more alias types. We expect more precise tagging from our slightly more rigorous solution.

@@

\begin{description}
\item[Derived words] According to the CoNLL guidelines, words derived from NEs are tagged as \texttt{MISC}. We complied with this rule by tagging each entity whose head is not a noun, as well as when the link's anchor text is not contained in the entity's name, as \texttt{MISC}. The most prominent example for such entities are nationalities, which can be linked to their home country, a \texttt{LOC}; e.g.~\textit{Turkish} to \textit{Turkey}. Our solution assigns the correct tag to these entities.
\item[First word in a sentence] As first words are always capitalized, labeling them is difficult if they are unlinked and not contained in the entity alias set. We base the decision on the POS tag of the first word: if it is \texttt{NNP}, we tag it as \texttt{UNK}; otherwise, \texttt{O}.
\item[Reference cleansing] Page titles and anchor texts may contain more than just the entity name. Personal titles are part of the entity name in Wikipedia, but not in CoNLL, and punctuation marks around the entity may become part of the link by mistake. We tag all punctuation marks after the entity name as \texttt{O}.
